%*******10********20********30********40********50********60********70********80

\chap{Introduction}


\section{Aim of the study}
Every single day in the world is produced a huge amount of data: some of this data, if they are analyzed and interpreted in the right way, could provide useful informations.\\
If we watch for example at the Aquaculture business in Norway is produced a big amount of data about every single locality or about national statistcs, but most of the time this data are not analyzed and difficult to understand.\\
The main purposes of this thesis are basically to test and show:
\begin{itemize} 
 \item 	Data potential in Aquaculture business in Norway through a system for analyzing and displaying data, in order to help the companies related with Aquaculture to improve their operations thanks to the analysis results.
 \item 	Python potential in data science, in order to show the people how it works and what you could do using it.
 \end{itemize}
For achieve the goals reported above, this thesis will provide:
\begin{itemize} 
 \item 	Implementation and description of a procedure that can be used for make a Python system able to do an initial analysis of  big datasets and also to display the obtained results.
 \item Implementation and description of a procedure that can be used for make a system implemented in Python able to predict future’s values using a regression model.
 
 \end{itemize}

\newpage
\section{Initial Goals}

\textbf{1) Collect as much data about aquaculture in Norway as possible.}
\vspace{-5mm}
\begin{itemize}
 \setlength{\itemsep}{-5pt}
  \item Which kind of data is possible to obtain about aquaculture general statistics in Norway? Where is possible to find it? Are that available for everyone?
  \item Which kind of data is possible to obtain about aquaculture of single locations in Norway? Where is possible to find it? Are that available for everyone?
\end{itemize}

 
\textbf{2) Increase accessibility and availability of the data.}
\vspace{-5mm}
\begin{itemize}
 \setlength{\itemsep}{-5pt}
  \item How you can create a unique dataset that contains and summarize all the data previous collected?
  \item Which kind of structure allows to the total dataset to be more accessable and readadble than the original single sources?
\end{itemize}
 
\textbf{3) Analyze and display the data.}
\vspace{-5mm}
\begin{itemize}
 \setlength{\itemsep}{-5pt}
  \item How it's possible to provide a general analysis and displaying of data about Norwegian aquaculture reported in the dataset?
  \item Which kind of Python functions is possible to use for analyze and displaying data? What is required and how is possible to implement it?
	\vspace{-3mm}
	\begin{itemize}
 	\setlength{\itemsep}{-5pt}
	\item Is Python a good programming language for data analysis and displaying?
	\item Does Python give the possibility to create analysis systems in easy way?
	 \end{itemize}
  \item Which kind of relationships and patterns about the data is possible to identify using the result graphics? How is possible to identify it?
  \item How is possible to check out the data trend line? 
  \item Which kind of informations have been reported for future reuse? How it's possible to access it? (Informations such as correlation coefficients, trend line equations,..)
 \end{itemize}


\textbf{4) Extract information from the data.}
\vspace{-5mm}
\begin{itemize}
 \setlength{\itemsep}{-5pt}
  \item Which parameters about aquaculture in Norway are increasing? How fast are they increasing/decreasing? 
  \item How you can compare different parameters trend line?
  \item Which kind of correlations is possible to find out between different parameters? How is possible to show it? What is possible to extract from that?
 \end{itemize}
 
 \newpage
 
\textbf{5) Prediction of values about the data.}
\vspace{-5mm}
\begin{itemize}
 \setlength{\itemsep}{-5pt}
  \item How is possible to predict some future values of the data that we own? 
		\vspace{-3mm}
		\begin{itemize}
 		\setlength{\itemsep}{-5pt}		
		  \item Would be useful to have the possibility of forecasting some future data?
		  \item Which kind of data might be the most useful to know for people into the Aquaculture field?
		 \end{itemize}
  \item Which Python utilities is possible to use for time series predictions?
  		\vspace{-3mm}
		\begin{itemize}
 		\setlength{\itemsep}{-5pt}	
		  \item How Python works for time series prediction systems implementation?
		  \item Which kind of accuracy it provides about the predicted values?
		  \item Would it be a good way for let the people get some experience with the machine learning field? 
		\end{itemize}
 \end{itemize}

\textbf{6) Recommendations to future work and extra ideas.}
\vspace{-5mm}
\begin{itemize}
\setlength{\itemsep}{-5pt}
	\item Which kind of services is possibl to provide using the collected informations and the implemented systems?
  		\vspace{-3mm}
		\begin{itemize}
 		\setlength{\itemsep}{-5pt}	
		  	\item How you can provide the analysis system like a service?
		  	\item How you can provide the prediction system like a service?
		\end{itemize}
 \end{itemize}




