%*******10********20********30********40********50********60********70********80

\chap{Introduction}


\section{Aim of the study}
Every single day in the world is produced a huge amount of data: some of this data, if they are analyzed and interpreted in the right away, could provide useful informations.\\
If we watch for example at the Aquaculture business in Norway is produced a big amount of data about every single locality or about national statistcs, but most of the time this data are not analyzed and difficult to understand.\\
The main purposes of this thesis are basically to test and show:
\begin{itemize} 
 \item 	Data potential in Aquaculture business in Norway through a system for analyzing and displaying data, in order to help the companies related with Aquaculture to improve their operations thanks to the analysis results.
 \item 	Python potential in data science, in order to show the people how it works and what you could do using it.
 \end{itemize}
For achieve the goals reported above, this thesis will provide:
\begin{itemize} 
 \item 	Implementation and description of a procedure that can be used for make a Python system able to do an initial analysis of  big datasets and also to display the obtained results.
 \item Implementation and description of a procedure that can be used for make a system implemented in Python able to predict future’s values using a regression model.
 \item List of possible implementation for further uses of machine learning algorithms and regression model.
 
 \end{itemize}

\newpage
\section{Initial Goals}

\textbf{1) Collect as much data about aquaculture in Norway as possible.}\\
- Is possible to obtain data about aquaculture general statistics in Norway?\\
- Is possible to obtain data about aquaculture of single locations in Norway?

 
\textbf{2) Increase accessibility and availability of the data.}\\
- Is that possible to create a unique dataset that contains all the data previous collected?\\
- Is the total dataset easier to access and read the new dataset structure compared with original single sources?

 
\textbf{3) Analyze and display the data.}\\
- Is that possible to provide a general analysis and displaying of data about Norwegian aquaculture reported in the dataset?\\
- Is that possible to use Python for analyzing and displaying the data?\\
	- Is Python a good programming language for data analysis and displaying?\\
	- Does Python give the possibility to create analysis systems in easy way?
- Are the obtained graphics allowing to comprehend information quickly?\\
- Are the obtained graphics allowing to identify relationships and patterns in a easy way?\\
- Are the obtained graphics allowing to identify historic and future trend line?\\
- Are the obtained informations (such as correlation coeff, trend line equations,..)reported in documents ready to be reused in the future?
 
\textbf{4) Extract information from the data.}	\\
- Is the aquaculture business in Norway growing? \\
- More in the specific, which parameters are increasing and how fast? \\
- Is that possible to have a trend line about the data? \\
- Is that possible to find some correlations between the data in input and display them? \\
- Are that data influenced from external parameters? Such as weather, news, people ideas..

 
\textbf{5) Prediction of values about the data.}\\
- Is that possible to predict some of the data that we own?\\
		- Would it be useful to have the possibility of forecasting some future data?\\
		- Which kind of data might be the most useful to know for people into the Aquaculture field?\\
-Test and describe time series predictions utility in Python.\\
		- Is Python a good way for time series prediction systems implementation?\\
		- Does it give the possibility to have accurate results?\\
		- Is that good for let the people get some experience with machine learning field?


\textbf{6) Recommendations to future work and extra ideas.}\\
- Is that possible to let the informations collected before be available like a service?\\
		- Is that possible to provide the analysis and prediction systems like a service?\\
		- Is that possible to let the data displaying dynamic instead of static?\\





