\chap{Discussion and Evaluations}
The results obtained are actually providing an answer to the initial questions of this thesis. In particular:

------> Initial approach with Data Science field, done?

- The working procedure that has been followed during this work allows to have an initial approach with the data science field, since have been reported INITIAL considerations about any step of the general data science process. ( Data colleciton, analysis, displaying, extraction, forecasting..)

------> Test the Python potential in Data Science field, done?
- The results reported during this thesis are actually showing the Python potential in data analysis, displaying and forecast.

------> Are the data about Norwegian salmon farming structured, described and readable?
- This study process actually changed the structure of the data. From the original data sources to the final dataset, with relative descriptions, graphics, coefficients,.. there is a big different that could be helpful for future reuse of the data for more specific analysis.

Interpret and explain your results

Answer your research question

Justify your approach

\section{Evaluation and limitations of the study}
- The implemented Python system can be reused for any kind of input dataset (with just the monthly frequency requirement).
It allows to make some analysis done during this thesis about other dataset in a fast and easy way.
 
- All the systems implemented in this thesis are probably efficient and productive for a personal use. That's because there is no GUI implemented and to customize the output graphics in a better way you have to know Python language.

- Not enough informations have been extracted from the data cause of a lack in the background theory about Norwegian salmon farming, and not enough time to document myself in a proper way.

- Not enough informations about machine learning field, so during this thesis was implemented just a basic implementation of the forecasting system, just to give an idea about how it works and give the possibility to improve it in future works.

The purpose of the discussion is to interpret and describe the significance of your findings in light of what was already known about the research problem being investigated, and to explain any new understanding or insights about the problem after you've taken the findings into consideration. The discussion will always connect to the introduction by way of the research questions or hypotheses you posed and the literature you reviewed, but it does not simply repeat or rearrange the introduction; the discussion should always explain how your study has moved the reader's understanding of the research problem forward from where you left them at the end of the introduction.
