\chapter{Results Overview}
This study provides several results, that are basically the implemented systems themselves and the generated evidences.\\
Since the big amount of evidences made during this work, below here is reported an overview of the final results. If you're interested to check out the whole results and even use it, it's possible to find it on the already citated Github repository. \footnote{System repository: https://github.com/Sprea22/Python\_Systems}

Further more you can find the Datasets collection and all the implemented python systems file.

\textbf{Results} - Contains several analysis results, basically all the outputs of SIA and MIA systems. In particular\\
Dataset X folder:
	A general folder that contains:
			- Correlation coeff between all the inputs
			- Document that contains the corr coeff values
			- Comparison graphic of the trend line normalized angular coefficients of all the inputs
			- Folder with all the inputs overview
	For each paramater of the current dataset is reported a folder that contains:\\
			- Document that contains trend line angular coefficeints and trend line normalized angular coefficient.\\	
			- Document that contains months correlation coefficients values\\
			- Document that contains years correlation coefficients values\\
			- Total graphic\\
			- Years graphic\\
			- Corr matrix between years\\
			- Corr matrix between month\\
			- Overview \\

\textbf{Results\_Forecast} - Contains several results about the forecasting system.
Dataset X folder: 
	For each paramater of the current dataset is reported a document that contains the evaluation results, so MAPE values for each ARIMA 	configuration tested.
		
\textbf{Results\_Maps} - Contains several results about the map system. In particular different cartographic map about Norway with different average inputs on a range of time between 2007 and 2014.
